---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Covid19Map

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/Covid19Map)](https://CRAN.R-project.org/package=Covid19Map)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
<!-- badges: end -->

The goal of Covid19Map is to download the Covid-19 time-series from Johns Hopkins University Github page. There are three functions in this package that can be used for getting a clean data, plotting a World-map showing the number of cases and death in each day and a final figure that shows time-series for any individual country during a user defined interval.

## Installation

You can install the released version of Covid19Map from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Covid19Map")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("hojjatks/Covid19Map")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(Covid19Map)
## basic example code
library(RCurl)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(stringr)
library(lubridate)
DataFrame<-GetFullTimeseries()
```




```{r pressure}
Covid19Map::PlotCountryTimeseries(FromDate="2020.2.1",
           ToDate="2020.10.20",
           Country="Iran",TypeP="New Death")
```

